---
title: "Tutorial 5, 2010"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(lubridate)
source('utils.R')
retail_clean <- readRDS('www/retail_clean.rds')
```

## Retail Transations, UK

The file `retail_clean.rds` contains transactions from an online gift store 
based in the United Kingdom. Here are more details about the columns in the 
dataset:

1. `InvoiceNo`: The invoice number for the transaction. Several items can be 
purchased under one invoice number.
2. `StockCode`: A warehouse code for the item purchased.
3. `Description`: A detailed description of the item purchased.
4. `Quantity`: Amount purchased by the customer.
5. `InvoiceDate`: Date of invoice.
6. `UnitPrice`: The unit price of the item purchased.
7. `CustomerID`: A unique identifier for the customer.
8. `Country`: The country that the customer is from.

We shall refer to each row in the dataset as a *line item*. The dataset has been
read into R, and is stored as the object: `retail_clean`. Use `dplyr` syntax to
carry out the following queries, using dplyr syntax.

The following libraries have been loaded into your R session:

* `lubridate`
* `tidyverse`

### Exercise 1

Extract all rows from the customer who *spent the most* over the time period.
Store the rows in a data frame (or tibble) called `q1_df`.

```{r q1, exercise=TRUE, exercise.lines = 5}
q1_df <- 

```

### Exercise 2 

Add two new columns to `retail_clean`: *year* and *month*, both numeric,
corresponding to the year and month from the Invoice Date. Count the number of
unique invoices in each year-month combination and arrange them in descending
order in a dataframe `q2_df`. 

The first few rows of data frame `q2_df` should look like this:
```
> head(q2_df)
# A tibble: 6 × 3
   year month     n
  <dbl> <dbl> <int>
1  2011    11  2631
2  2011    10  1883
3  2011     9  1728
4  2011     5  1529
5  2010    12  1385
6  2011     6  1376
```

```{r q2, exercise=TRUE, exercise.lines = 5}
q2_df <- 
```

### Download your solution

Remember to run all your code before you download your script, and do check the
script to ensure that all your code is present before you submit.

```{r context='render', echo=FALSE, eval=TRUE}
downloadLink("download", "Download my solution script")
```

```{r context='server', echo=FALSE, eval=TRUE}
all_labels <- c("q1", "q2") 
# 1 - chunk
# 2 - text
ex_text <- c(1, 1)

output$download <- downloadHandler(
    filename = "my_soln.Rmd",
    content = function(file) { 
      init_rmd(file, "My solution")
      
      # libraries read in
      add_libraries(file, c("tidyverse", "lubridate"))
      
      # data read in:
      data_chunk <- 'retail_clean <- readRDS("www/retail_clean.rds")'
      add_chunk_rmd(file, "read_data", data_chunk)
      
      for(ii in seq_along(all_labels)){
        if(ex_text[ii] == 1){ # chunk
          tut_state <- get_tutorial_state(all_labels[ii])
          add_chunk_rmd(file, all_labels[ii], tut_state$answer, 
                        add_tryCatch = TRUE)
        } else {
          add_text_rmd(file, all_labels[ii], input[[all_labels[ii]]])
        }
        
      }
    }
)

```

